Supporting Ecological Decision Making Using Feature-Selection and Variable Importance

### 2019-08-31 code/98-paper/ieee/ieee-manuscript.tex
optimize results - performance

\section{Discussion}

>>>>

% - RMSE around 34
% - MBO tuned penalized methods are substantially worse
% - Carscore, Info und Borda were at least once among the best combination for a learner
\noindent No practical differences in RMSE were observed among the feature sets (\autoref{fig:perf-result}).
SVM showed the lowest error in four out of six tasks.
Overall, the response variable "defoliation at trees" could be modeled with an error of 34 \%.

% tasks
% - no substantial difference between feature sets
% - combining feature sets makes no difference
% - expert based feature sets show no better result than data-driven ones
% - penalized methods seem to have problems with VI feature set
No practical difference was observed between feature sets.
The combination of feature sets showed no increase in performance.
All learners scored evenly across all tasks.
Feature sets containing expert-based variables (VI) showed no substantial difference to data-driven tasks (NRI).

% learner
% - RF Car is the overall winner
% - Ridge-CV hit and miss (hit = NRI, miss = VI)
% - all MBO penalized methods have no difference across tasks
Random Forest combined with the "Carscore" filter showed the best absolute performance (RMSE of 3.396).
A noticable difference between SVM and all other learners was visible for all feature sets without NRI variables (difference in RMSE of 3-4).
L1 penalized regression showed slightly better results in three out of six tasks when being optimized using the package internal 10-fold CV compared to MBO (RMSE of 50 vs 58).
Regression with Ridge penalty showed a high variance when comparing results across tasks: In three out of six tasks (all including VI variables) the error was out of bounds (HR-NRI-VI; HR-VI, VI), for HR-NRI and HR the error was medium (around 40 RMSE), and for task NRI Ridge regression achieved almost the same score as the best performing model (3.39 RMSE, NRI).
All penalized methods tuned using MBO showed exactly the same error across all tasks.

% filters
% - influence varies based on algorithm
% - no substantial improvement on these datasets compared to no filter
% - no substantial descrese in performance
% - no advantage of ensemble borda filter compared to others
Differences between filter methods were neglibly small in this study.
Ensemble filters showed no substantial difference to simple filter methods.
However, there was also no change to worse when using filter methods compared to using none.
Comparing absolute values, filters "Carscore", "Information gain" and the "Borda" ensemble filter scored the best results across all learners and tasks.

\begin{figure} [t!]
\centering
	\begin{center}
		\includegraphics[width=0.5\textwidth] {performance-results-1.pdf}
        \caption{Scored predictive performance (RMSE) of models across tasks. Prefix "CV" denotes that the learner was optimized using internal 10-fold CV while prefix "MBO" means that Bayesian optimization was used for hyperparameter optimization. The abbreviations on the y-axis refer to the combinations of feature sets on which each model was scored on. Labels attached to each point in space show which filter method was used for scoring features during the feature selection process (NF = no filter, Car = "Carscore", Info = "Information Gain", Borda = "Borda"). The second value in the attached label of each point shows the scored RMSE value of the respective setting.}
		\label{fig:perf-result}
	\end{center}
\end{figure}
\section{Discussion}
